---
title: "deKort 2020 Recreation, Figure 2"
author: "Jill Syrotchen"
date: "11/16/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Step 1: locating data
-Finding the data was extremely easy - all I needed to do was click on the URL to the DRYAD repository that the authors put in the Data Availability section near the end of the paper. In the repository was a single .xlsx file that contained the full dataset.  
-Code was not available.  
-The paper did mention specific R packages used to analyze results - in this case, the package "Plasticity" - but offered no more than a mention.

###Step 2: Github and loading data
-I created a Github repository for this recreation project (https://github.com/jillsyro/DST-deKort).  
-I converted the .xlsx file with data to a .csv file and added it to my project folder to bring in the data.  

###Step 3: Loading data and packages
```{r Loading data, include=TRUE, message=FALSE}
#install.packages("Plasticity")
#library("Plasticity")
library("tidyverse")
library("ggplot2")
library("magrittr")
library("knitr")

full_dataset<-read_csv("./data/Dryad_JEcol-2019-0718.csv")

```
-I ran into a problem while trying to install the Plasticity package (code commented out). It gave me the error "Warning in install.packages :
  package ‘Plasticity’ is not available (for R version 4.0.2)".  
-I googled "r package plasticity" and the first result was this Github page (https://github.com/ameztegui/Plasticity) for the package. In the readme file was different instruction for loading the package:
```{r Installing Plasticity package, include=TRUE, message=FALSE}
library("devtools")
#devtools::install_github("ameztegui/Plasticity")

#Dependencies I did not have installed
library("agricolae")
library("psych")
```
-After installing the devtools package, the line of code provided in the readme file to install the Plasticity package worked! It is commented out to allow for knitting to PDF, but the # should be removed to install the package and run the code.
-The readme file also had a section for dependencies to run the Plasticity package, so above I installed the packages I did not already have installed.  